\documentclass[8pt]{resume}

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\usepackage{hyperref}

\name{Yixin Lin}
\address{(510) 730-0186 \\ yixin@yixinlin.net \\ {\it yixinlin.net} \\ {\it github.com/1heart} \\ {\it linkedin.com/in/linyixin}}

\begin{document}
\begin{rSection}{Profile}
  Research engineer in robot learning at Meta AI, interested in sample-efficient reinforcement learning for embodied AI.
\end{rSection}

\begin{rSection}{Education}

{\bf Duke University} \hfill {\em Graduated May 2018} \\
\/ B.S. in Computer Science -- Overall GPA: 3.944/4.000, Major GPA: 4.000/4.000

{\bf Relevant coursework}
{\it
  Artificial Intelligence | Algorithms | Bayesian statistics | Advanced linear algebra |
  Computer vision | Advanced machine learning | Complexity theory | Computational microeconomics | DNA computation
}
\end{rSection}

\begin{rSection}{Professional Experience}

  \begin{rSubsection}{Meta AI (formerly Facebook AI Research)}{September 2018 - September 2021; September 2021 - Present}{Research engineer}{Menlo Park, CA; New York, NY}
  Published research in model-based reinforcement learning for robotic control accepted to top robotics conferences. Leads real-time capable C++ controller stack built upon PyTorch/Torchscript.
  \begin{itemize}
    \item Jain, V., Lin, Y., Undersander, E., Bisk, Y., \& Rai, A. (2022). Transformers are Adaptable Task Planners. arXiv preprint arXiv:2207.02442.
    \item Shankar, T., Lin, Y., Rajeswaran, A., Kumar, V., Anderson, S., \& Oh, J. (2022). Translating Robot Skills: Learning Unsupervised Skill Correspondences Across Robots. In International Conference on Machine Learning (ICML).
    \item Lin, Y., Wang, A. S., \& Rai, A. (2021). Efficient and Interpretable Robot Manipulation with Graph Neural Networks. arXiv preprint arXiv:2102.13177. In IEEE Robotics and Automation Letters, International Conference on Robotics and Automation 2022.
    \item Bechtle, S., Lin, Y., Rai, A., Righetti, L., \& Meier, F. (2020, May). Curious ilqr: Resolving uncertainty in model-based rl. In Conference on Robot Learning (pp. 162-171). PMLR.
    \item Sutanto, G., Wang, A., Lin, Y., Mukadam, M., Sukhatme, G., Rai, A., \& Meier, F. (2020). Encoding physical constraints in differentiable newton-euler algorithm. In Learning For Dynamics \& Control 2020.
    \item Meier, F., Wang, A. S., Sutanto, G., Lin, Y., Shah, P. (2022), Differentiable and Learnable Robot Models. In Journal of Machine Learning Research (JLMR).
    \item Dasari, S. et al. RB2: Robotic Manipulation Benchmarking with a Twist. In Neural Information Processing Systems 2021, Datasets and Benchmarks Track.
    \item Morse, K., Das, N., Lin, Y., Wang, A., Rai, A., \& Meier, F. (2020). Learning State-Dependent Losses for Inverse Dynamics Learning. In International Conference on Intelligent Robots and Systems 2020.
  \end{itemize}
\end{rSubsection}

\begin{rSubsection}{Google Brain Robotics}{October - December 2017}{Software engineering/machine learning intern}{Mountain View, CA}
\item Worked on characterizing the optimization landscape of deep reinforcement learning and implications for learning and convergence
\item Supervised by Eric Jang (\textbf{Google Brain}), Oriol Vinyals (\textbf{Google DeepMind})
\end{rSubsection}


\begin{rSubsection}{Facebook Applied Machine Learning (AML)}{May - August 2017}{Software engineering/machine learning intern}{Menlo Park, CA}
\item Improved \textbf{world's largest deep learning facial recognition system} through Gaussian augmentation strategy (reduced recall error by \textbf{10\%}), increased model training rate by \textbf{10x}, implemented frontalizing \textbf{GAN}; used \textbf{Lua/Torch, Python/PyTorch, Java, C++, SQL}
\item Supervised by Dr. Fernando de la Torre (professor at \textbf{Carnegie Mellon}, research scientist manager at \textbf{Facebook})
\end{rSubsection}

% \begin{rSubsection}{Advances of Machine Learning in Theory \& Applications
%  (AMALTHEA), Florida Tech}{May - July 2016}{Machine learning researcher}{Melbourne, FL}
% \item Extending 3D shape
%   retrieval using wavelet density estimation with multi-res wavelets: \url{yixinlin.net/amalthea/report.pdf}
% \end{rSubsection}

\begin{rSubsection}{Contrary Capital}{May 2016 - Present}{Founding student partner \& Contrary Talent Fellow}{}
\item Source deals, complete due diligence, and make investment recommendations for \textbf{decentralized, university-focused venture fund}
\item Member of \textbf{select, diverse community} of the top early-career engineers, designers, and product minds working in technology.
\end{rSubsection}

\begin{rSubsection}{Gusto (formerly ZenPayroll)}{May - August 2015}{Software engineering intern, KPCB Engineering Fellow}{San Francisco, CA}
\item Part of \textbf{KPCB Fellows} program (see {\it kpcbfellows.com/about}), \textbf{3\%} acceptance rate
\item Contributed to \textbf{React/Flux/AngularJS/Rails} stack, built fraud-ring detection tool used by Risk Team, \textbf{prevented \$10k+ in losses}
\item Integrated \textbf{Neo4J} with real-time relational database synchronization, built graph visualization with \textbf{React} and \textbf{vis.js}
\end{rSubsection}

\end{rSection}

\begin{rSection}{Academic experience}

\begin{rSubsection}{Reviewer}{}{}{}
\item Reviewer for International Conference on Robotics and Automation (ICRA), IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), \& NeurIPS (workshop on Physical Reasoning and Inductive Biases for the Real World).
\end{rSubsection}

\begin{rSubsection}{Duke University - AI Policy research}{January-May 2018}{Independent researcher}{Durham, NC}
\item Co-authored white paper on US policy on AI leadership and provides policy recommendations: \url{aipolicy.us/whitepaper.pdf}
\item Presented white paper in Washington, D.C. to offices of \textbf{Senator Maria Cantwell}, \textbf{Congressman John Delaney}
\end{rSubsection}

\begin{rSubsection}{Duke University -- Carin lab, Information Initiative at Duke (iiD)}{August 2016 - August 2017}{Machine learning researcher}{Durham, NC}
\item Applied matrix factorization methods to optimization in \textbf{deep learning} to improve gradient descent, investigated multi-agent language acquisition through \textbf{deep reinforcement learning}, advised by Dr. Lawrence Carin and Dr. Xuejun Liao
\end{rSubsection}

\end{rSection}

\end{document}
